Impact of grids and dynamical cores in CESM2.2 on the meteorology and climate of the Arctic

### 2021-05-13 arcticgrids.tex
zwally basin figure
new racmo version in fig 6

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_PRECT.pdf}
\end{center}
\caption{.}
\label{fig:prect}
\end{figure}

@@

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_diffRACMO23p2_5p5km.pdf}
\end{center}
\caption{Climatological (1979-1998) annual precipitation rate bias relative to the RACMO3.2p2 5.5km resolution data product \cite{NETAL2019SCIENCE}.}
\label{fig:prect}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_BASIN_uqmap.pdf}
\end{center}
\caption{.}
\label{fig:zwally}
\end{figure}
